Open-source tools in R for landscape ecology

### 2021-01-22 paper/paper.Rmd
added movement packages
add in spatial stats section to the table

>>>>

\multirow{6}{*}{\shortstack[l]{Spatial statistics}} & spatstat & Point pattern analysis & \cite{R-spatstat} \\
& spdep & Quantify and correct for spatial autocorrelation & \cite{Bivand2013} \\
& rinla & Fitting Bayesian spatio-temporal models using INLA & \cite{rue2009approximate} \\
& inlabru & Fitting Bayesian spatio-temporal models using INLA & \cite{R-inlabru} \\
& geoR & Variograms, correlograms and (co-)kriging & \cite{R-geoR} \\
& gstat & Variograms, correlograms and (co-)kriging & \cite{R-gstat} \\
